%%%%%%%%%%%%%%%%%%%%%%% file globs.tex %%%%%%%%%%%%%%%%%%%%%%%%%
%
% This is a general template file for the LaTeX package SVJour3
% for Springer journals.          Springer Heidelberg 2010/09/16
%
% Copy it to a new file with a new name and use it as the basis
% for your article. Delete % signs as needed.
%
% This template includes a few options for different layouts and
% content for various journals. Please consult a previous issue of
% your journal as needed.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\RequirePackage{fix-cm}
%
%\documentclass{svjour3}                     % onecolumn (standard format)
%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
\documentclass[smallextended]{svjour3}       % onecolumn (second format)
%\documentclass[twocolumn]{svjour3}          % twocolumn
%
\smartqed  % flush right qed marks, e.g. at end of proof
%

\makeatletter
%\def\cl@chapter{\cl@chapter \@elt {theorem}}%bug in class
\def\cl@chapter{\@elt {theorem}}
\makeatother

\usepackage{natbib}

\usepackage{amsmath,amsfonts}
\usepackage{array}
\usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
\usepackage{url}
\usepackage{graphicx}
\usepackage{mathptmx}      

\usepackage{cleveref}

\usepackage[utf8]{inputenc}
\usepackage{listingsutf8, pythonhighlight}
\lstset{ 
literate= {á}{{\'a}}1 
    {é}{{\'e}}1 
    {í}{{\'i}}1 
    {ó}{{\'o}}1 
    {ú}{{\'u}}1
} 

\usepackage{listings, lstautogobble}
\usepackage{xspace}
\usepackage{booktabs}
\usepackage{xcolor}

\lstdefinelanguage{JavaScript}{
    keywords={typeof, new, true, false, catch, function, return, null, catch, switch, var, if, in, while, do, else, case, break},
    keywordstyle=\color{blue}\bfseries,
    ndkeywords={class, export, boolean, throw, implements, import, this},
    ndkeywordstyle=\color{darkgray}\bfseries,
    identifierstyle=\color{black},
    sensitive=false,
    comment=[l]{//},
    morecomment=[s]{/*}{*/},
    commentstyle=\color{gray}\ttfamily,
    stringstyle=\color{red}\ttfamily,
    morestring=[b]',
    morestring=[b]"
}

\lstdefinelanguage{HCL}{
    keywords={path, capabilities, read, write},
    keywordstyle=\color{blue}\bfseries,
    sensitive=false,
    comment=[l]{\#},
    commentstyle=\color{gray}\ttfamily,
    stringstyle=\color{red}\ttfamily
}

\lstdefinelanguage{Go}{
    keywords={func, const, if, else, return, nil, error, string},
    keywordstyle=\color{blue}\bfseries,
    sensitive=false,
    comment=[l]{//},
    morecomment=[s]{/*}{*/},
    commentstyle=\color{gray}\ttfamily,
    stringstyle=\color{red}\ttfamily
}

\lstset{
    basicstyle=\ttfamily\small,
    breaklines=true,
    frame=single,
    backgroundcolor=\color{gray!10},
    captionpos=b
}
\lstdefinelanguage{ebnf}{
    morekeywords={::=},
    sensitive=false,
    morecomment=[l]{//},
    morecomment=[s]{/*}{*/},
    escapeinside={(@}{@)},
}
\lstset{
    basicstyle=\ttfamily\small,
    keywordstyle=\color{blue},
    commentstyle=\color{gray},
    stringstyle=\color{red},
    breaklines=true,
    frame=single,
    backgroundcolor=\color{gray!10},
    captionpos=b
}

\usepackage{enumitem}
\setlist[itemize]{noitemsep, topsep=3pt}
\newlist{researchquestions}{enumerate}{1}
\setlist[researchquestions]{label*=\textbf{RQ\arabic*}}


\newcommand{\todo}[1]{{\color{red}#1}}
\newcommand{\evaluate}[1]{{\color{blue}#1}}

\newcommand{\tab}{\hspace*{0.3cm}}

\newcommand{\eg}{\hbox{\emph{e.g.}}\xspace}
\newcommand{\ie}{\hbox{\emph{i.e.}}\xspace}
\newcommand{\etc}{\hbox{\emph{etc.}}\xspace}
\newcommand{\vs}{\hbox{\emph{vs.}}\xspace}
\newcommand{\st}{\hbox{\emph{s.t.}}\xspace}
\newcommand{\wrt}{\hbox{\emph{w.r.t.}}\xspace}

\newcommand{\gdos}{\hbox{G-DoS}\xspace}

\newcommand{\cf}[1]{\texttt{#1}}

\newcommand\bnfalt{\;\;|\;\;}
\newcommand\bnfas{\;\;:=\;\;}

% Insert the name of "your journal" with
\journalname{Empirical Software Engineering}
%
\begin{document}

\title{An Empirical Analysis of the Glob Ecosystem}

\author{Phyllis Lim         \and
        Connor Adkins       \and
        Mark Marron
}

%\authorrunning{Short form of author list} % if too long for running head

\institute{Phyllis Lim \at
              \email{pli231@uky.edu}
            \and
            Connor Adkins \at
              \email{chandon.adkins@uky.edu}
            \and
            Mark Marron \at
              \email{mark.marron@uky.edu}
}

\date{Received: date / Accepted: date}
% The correct dates will be entered by the editor

\maketitle

\begin{abstract}
Glob patterns, a domain-specific language for structured string matching, are a foundational yet understudied component of modern software development embedded in everything 
from build scripts and configuration files to web server routes. However, this widespread use, rests on a fragile foundation. Despite their ubiquity across operating system tools 
and programming languages, a lack of standardization has led to a fragmented ecosystem rife with inconsistent behaviors, security vulnerabilities, and usability pitfalls. 
This paper presents the first empirical study of the glob ecosystem to quantify these challenges and chart a path toward robust solutions. 

Through an analysis of $1,966$ open source projects, $1,355$ Github issues, $444$ CVE reports, and $361$ StackOverflow posts, we systematically map the feature support and 
real-world usage of globs across six common ecosystems that utilize globs. 
Our findings reveal a stark divide between various globbing implementations and developer adoption. In addition, we document inconsistencies that hinder portability, reliability, 
and create security flaws. Our analysis reveals that security vulnerabilities are not corner cases, but a dominant concern, comprising almost a quarter of all developer discussions. 
We propose a path forward through standardization and introduce a formal grammar for \textit{GlobSpec}, a unified specification designed to resolve semantic ambiguities and 
bridge the expressiveness gap between current implementations and developer requirements.
\keywords{Globs, Pattern matching, Domain Specific Language, Software engineering}
% \PACS{PACS code1 \and PACS code2 \and more}
\subclass{MSC code1 \and MSC code2 \and more}
\end{abstract}

\section{Introduction}
\label{intro}
\input{intro.tex}

\section{Background}
\label{background}
\input{background.tex}

\section{Research Questions}
\label{sec:researchquestions}
\input{rqs.tex}

\section{Methodology}
\label{sec:methodology}
\input{methodology.tex}

\section{Analysis}
\label{sec:analysis}
\input{analysis.tex}

\section{Discussion}
\label{sec:discussion}
\input{discussion.tex}

\section{Threats to Validity}
\label{sec:threats}
\input{threats.tex}

\section{Related Work}
\label{sec:relatedwork}
\input{related.tex}

\section{Conclusion}
This study provides the first comprehensive analysis of globbing features across programming languages, highlighting inconsistencies, limitations, and areas for improvement. By 
examining real-world usage and cross-platform challenges, we identify the need for standardized implementations and enhanced developer tools to address portability and usability issues.
While globbing is a convenient mechanism for matching file paths, multiple vulnerabilities suggest it can become a surprising attack surface. We highlight Glob-Driven Denial-of-Service 
(\gdos) attacks as an emerging class of vulnerabilities where misuse of glob syntax or poor implementation leads to resource exhaustion, memory leaks, or crashes. Additionally, 
this work proposes a standardization for glob languages that unifies and simplifies many challenges present with existing globbing systems.
These findings lay the groundwork for better practices, opportunities for enhancements to the design, and standardization of globbing semantics, ultimately aiming to provide developers 
with robust, portable, and reliable capabilities. 

\section*{Data-Availability Statement}
The data used in this study, including the glob corpus, forum posts, and CVE issues is available via github (\url{xxxx}) as an evolving community data set and as a stable 
reproduction package at \todo{yyy} (\url{zzz}).

%\begin{acknowledgements}
%If you'd like to thank anyone, place your comments here
%and remove the percent signs.
%\end{acknowledgements}


% Authors must disclose all relationships or interests that 
% could have direct or potential influence or impart bias on 
% the work: 
%
% \section*{Conflict of interest}
%
% The authors declare that they have no conflict of interest.


% BibTeX users please use one of
%\bibliographystyle{spbasic}      % basic style, author-year citations
%\bibliographystyle{spmpsci}      % mathematics and physical sciences
%\bibliographystyle{spphys}       % APS-like style for physics

\newpage

\bibliographystyle{spbasic}
\bibliography{bibliography}

\end{document}
% end of file template.tex

