\documentclass{article}

\title{An Empirical Analysis of the Glob Ecosystem}
\author{Phyllis Lim \and Connor Adkins \and Mark Marron}
\date{}

\usepackage{url}

\begin{document}

\maketitle
\vspace{-7mm}

\begin{abstract}
    Glob patterns, a domain-specific language for structured string matching, are a foundational yet understudied component of modern software development embedded in everything 
from build scripts and configuration files to web servers. However, this widespread use rests on a fragile foundation. Despite their ubiquity across tools 
and programming languages, a lack of standardization has led to a fragmented ecosystem rife with inconsistent behaviors, security vulnerabilities, and usability pitfalls. 
This paper presents the first empirical study of the glob ecosystem to quantify these challenges and chart a path toward robust solutions. 

Through an analysis of $1,966$ open source projects, $1,355$ Github issues, $444$ CVE reports, and $361$ StackOverflow posts, we systematically map the feature support and 
real-world usage of globs across six common ecosystems that utilize globs. 
Our findings reveal a stark divide between various globbing implementations and developer adoption. In addition, we document inconsistencies that hinder portability, reliability, 
and create security flaws. Our analysis reveals that security vulnerabilities are not corner cases, but a dominant concern, comprising almost a quarter of all developer discussions. 
We propose a path forward through standardization and introduce a formal specification for globs, \textit{GlobSpec}, designed to resolve semantic ambiguities and 
bridge the expressiveness gap between current implementations and developer requirements.
\end{abstract}

\section*{Keywords}
Globs, Pattern Matching, Domain Specific Language, Software Engineering

\section*{Statements and Declarations}
No funding was received for conducting this study. The authors have no relevant financial or non-financial interests to disclose.

\section*{Data-Availability Statement}
The data used in this study, including the glob corpus, forum posts, and CVE issues is available via github (\url{https://anonymous.4open.science/r/glob-artifact-AA95}) as an evolving community data set and as a stable 
reproduction package at Zenodo, (\url{https://doi.org/10.5281/zenodo.18462402}).

\end{document}